---
output: 
  html_document:
    css: www/styles.css
title: "SACN Redundancy Analysis" 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
options(knitr.kable.NA = '')
options(width = 10)
```

## Lake St. Croix Water Quality Redundancy Analysis {.tabset}
### Background {.tabset}
#### Project Info
This document compares data collected in Lake St. Croix by the Great Lakes Network (GLKN) as part of their <a href="https://www.nps.gov/im/glkn/water-quality-rivers.htm">Water Quality (Rivers)</a> monitoring protocol with data collected by the <a href="https://metrocouncil.org/About-Us/What-We-Do/Departments/Environmental-Services.aspx">Metropolitan Council's Environmental Services (METC) Department</a>. 

For GLKN, we used the most recently published <a href="https://irma.nps.gov/DataStore/Reference/Profile/2309369">2006 -- 2024 Large Rivers Water Quality Monitoring Data</a> Data Package (IRMA record 2309369). For METC, we downloaded all data from 2006 and later from the METC's <a href="https://eims.metc.state.mn.us/AdvancedSearch">Environmental Information Management Systems (EIMS)</a> web server for all monitoring locations within Lake St. Croix. 

Based on the <a href="https://dashboard.waterdata.usgs.gov/app/nwd/en/">USGS National Water Dashboard</a>, Lake St. Croix is bounded by two USGS stream gages, which can be used to model discharge. USGS 05341550 is at the start of Lake St. Croix, very close to METC_STCR_23.6; USGS 05344490 is at the confluence near METC_STCR_0.1 and SACN_STCR_2.0.   

All code use for this analysis are posted on GitHub in the following repository: <a href="https://github.com/KateMMiller/GLKN_MCES_analysis">https://github.com/KateMMiller/GLKN_MCES_analysis</a>


Sites included in this analysis are plotted in the map below.
```{r echo = F, warning = F, message = F, results = 'hide'}
library(dataRetrieval)
gages <- c("05341550", "05344490")
gage_params <- c("00060", "00010", "00400") # Discharge, Temp, pH
gagedat <- whatNWISdata(siteNumber = gages, parameterCd = gage_params, service = 'dv')[,c("site_no", "parm_cd", "dec_lat_va", "dec_long_va", "begin_date", "end_date")]
gagedat$param[gagedat$parm_cd == "00060"] <- "Discharge"
gagedat$param[gagedat$parm_cd == "00010"] <- "Temp"
gagedat$param[gagedat$parm_cd == "00040"] <- "pH"
gagedat$Location_ID[gagedat$site_no == gages[1]] <- "USGS_STCR_23.5"
gagedat$Location_ID[gagedat$site_no == gages[2]] <- "USGS_STCR_0.2"
gagedat$Org_Code <- "USGS"
names(gagedat)[names(gagedat) == "dec_lat_va"] <- "Latitude"
names(gagedat)[names(gagedat) == "dec_long_va"] <- "Longitude"
# dv = daily values; uv = instantaeous value; qw = water quality
```

```{r echo = F, warning = F, message = F, results = 'hide'}
# Code for leaflet map
library(tidyverse)
library(sf)
library(leaflet)
library(leaflet.extras)
library(waterGLKN)
river_zip = "../data/GLKN_water/records-2309369.zip"
importData(type = 'zip', filepath = river_zip)
lksc <- c("SACN_STCR_20.0", "SACN_STCR_15.8", "SACN_STCR_2.0")
sacn_locs <- getLocations(site = lksc) |> select(Location_ID, Org_Code, Latitude, Longitude)
metc_locs1 <- read.csv("./data/local/2025-03-18_1359_56_MCES_EIMS_data.csv") |> 
  select(STATION_ID, X = X_COORDINATE_UTM, Y = Y_COORDINATE_UTM) |> unique() |> 
  mutate(Location_ID = case_when(grepl("SC0003", STATION_ID) ~ as.character("METC_STCR_0.1"),
                                 grepl("SC0233", STATION_ID) ~ as.character("METC_STCR_23.6"),
                                 grepl("SC0234", STATION_ID) ~ as.character("METC_STCR_23.4"),
                                 grepl("82000100-08", STATION_ID) ~ as.character("METC_STCR_22.5"),
                                 grepl("82000100-06", STATION_ID) ~ as.character("METC_STCR_11.3"),
                                 grepl("82000100-03", STATION_ID) ~ as.character("METC_STCR_16.6"),
                                 grepl("82000100-05", STATION_ID) ~ as.character("METC_STCR_12.4"),
                                 grepl("82000100-04", STATION_ID) ~ as.character("METC_STCR_15.3"),
                                 grepl("82000100-01", STATION_ID) ~ as.character("METC_STCR_22.3"))) |>
  filter(!is.na(Location_ID)) 

metc_sf <- st_as_sf(metc_locs1, coords = c("X", "Y"), crs = 32615)
metc_dd <- st_transform(metc_sf, crs = 4269)
metc_locs <- data.frame(Location_ID = metc_dd$Location_ID, 
                        Org_Code = "METC",
                        Latitude = st_coordinates(metc_dd)[,2], 
                        Longitude = st_coordinates(metc_dd)[,1])

samp_locs <- rbind(sacn_locs, metc_locs, gagedat[,c("Location_ID", "Org_Code", "Latitude", "Longitude")])
samp_sf <- st_as_sf(samp_locs, coords = c("Longitude", "Latitude"), crs = 4269)
samp_bb <- st_bbox(samp_sf)
cent_lat <- mean(samp_locs[,"Latitude"])
cent_long <- mean(samp_locs[,"Longitude"])

# leaflet basemaps
NPSbasic <- "https://atlas-stg.geoplatform.gov/styles/v1/atlas-user/ck58pyquo009v01p99xebegr9/tiles/256/{z}/{x}/{y}@2x?access_token=pk.eyJ1IjoiYXRsYXMtdXNlciIsImEiOiJjazFmdGx2bjQwMDAwMG5wZmYwbmJwbmE2In0.lWXK2UexpXuyVitesLdwUg"

ESRIimagery <- "http://services.arcgisonline.com/arcgis/rest/services/World_Imagery/MapServer/tile/{z}/{y}/{x}"

ESRItopo <- "http://services.arcgisonline.com/arcgis/rest/services/World_Topo_Map/MapServer/tile/{z}/{y}/{x}"

ESRINatGeo <- "http://services.arcgisonline.com/arcgis/rest/services/NatGeo_World_Map/MapServer/tile/{z}/{y}/{x}"

# Legend html generator
# Source: https://stackoverflow.com/questions/47064921/leaflet-legend-for-addawesomemarkers-function-with-icons
# Icon library changed from font-awesome to ion

markerLegendHTML <- function(IconSet) {
    # Container div:
    legendHtml <- "<div style='padding: 10px; padding-bottom: 10px;'>
    <h4 style='padding-top:0; padding-bottom:10px; margin: 0; color:#555'> Legend </h4>" #legend title

    n <- 1
    # Add each icon for ion library icons:
    for (Icon in IconSet) {
        if (Icon[["library"]] == "ion") {
        legendHtml<- 
          paste0(legendHtml,
          # marker and marker label div
          "<div style='width: auto; height: 45px; display: flex; align-items: center;'>",
          # awesome marker div
          "<div style='position: relative; display: inline-block; width: 35px; height: 45px;' 
          class='awesome-marker-icon-", Icon[["markerColor"]]," awesome-marker'>",
          # add icons and set color
          # class='ion ion-waterdrop icon-white' selects the correct library, icon, and color
          "<i style='margin-left: 4px; margin-top: 11px' class= 'ion ion-",
            Icon[["icon"]]," icon-", Icon[["iconColor"]],"'></i>",
          "</div>", # close awesome marker div
          # legend label div - use name set in IconSet
          "<div style='position: relative; display: inline-block; margin-left: 8px;'>", 
            names(IconSet)[n] ,"</div>",
          "</div>") # close marker/marker label div    
        }
        n <- n + 1
    } 
    paste0(legendHtml, "</div>")
}

# Create list of icons to use in map
IconSet <- awesomeIconList(
  "METC" = makeAwesomeIcon(icon= 'waterdrop', markerColor = 'lightblue', iconColor = 'white', library = "ion"),
  "GLKN" = makeAwesomeIcon(icon= 'waterdrop', markerColor = 'cadetblue', iconColor = 'white', library = "ion"),
  "USGS" = makeAwesomeIcon(icon= 'waterdrop', markerColor = 'green', iconColor = 'white', library = "ion")
)

# Create leaflet map
leaf <- 
leaflet(height = 650, width = 800) |> 
    # set default view of park
    setView(lng = cent_long,
            lat = cent_lat, 
            zoom = 10.25) |> 
    # add map tiles
    addTiles(group="Map", urlTemplate = NPSbasic) |> 
    addTiles(group="Imagery", urlTemplate = ESRIimagery)  |> 
    addTiles(group="Topo", urlTemplate = ESRItopo)  |> 
    addTiles(group="NatGeo", urlTemplate = ESRINatGeo)  |> 
    # add button to control map tiles
    addLayersControl(baseGroups = c("Map","Imagery","Topo", "NatGeo"),
                     options = layersControlOptions(collapsed=T)) %>%
    # add site markers 
    addAwesomeMarkers(data = samp_locs, ~Longitude, ~Latitude, 
                      icon = ~IconSet[Org_Code], #style markers based on site type
                      # label on mouseover
                      label=as.character(samp_locs$Location_ID),
                      labelOptions = labelOptions(noHide = T, textsize = "12px", textOnly = T, 
                                                  direction = 'right', offset = c(10,-5),
                                                  style = list("color" = "black", "font-weight" = "bold")),# offset = c(-10,-5)),
                      # popup on click
                      popup = paste0("<b>Site: ", samp_locs$Location_ID, "</b><br>",
                                     "<b>Org_Code: </b>", samp_locs$Org_Code, "<br>")) |> 
    # add legend
    addControl(markerLegendHTML(IconSet = IconSet), position = "bottomleft") |> 
    addResetMapButton()


```
```{r echo = F, warning = F, message = F}
leaf
```


#### Code Prep
<h4> Install waterGLKN R package </h4>
The waterGLKN package is still a WIP, but at least makes it easier to import and query of GLKN water data using the format of the latest rivers and inland lakes data packages. Must also have RTools44 installed, which can be installed via the Software Center, and the devtools R package. 
```{r echo = T, eval = F}
devtools::install_github("katemmiller/waterGLKN")
library(waterGLKN)
```

```{r include = F}
library(waterGLKN)
```

<h4> Troubleshooting github-installed packages:</h4>
If you’re unable to install the R package via GitHub (often an error about permission being denied, download the following script and open it in R: <a href="https://doimspp-my.sharepoint.com/:u:/g/personal/kmmiller_nps_gov/ETaknusoEfVOs9tbIbx6QYEBre0WI-_xxi-C0M3JCX_xfw?e=3XAXiC">fix_TLS_inspection.R</a>

Once open in R Studio. Press Control + A to select all of the code. Then Control + Enter to run all of the code. Assuming you don’t return any errors, you should now be able to install from GitHub. Repeat the install_github code above, which hopefully will successful install waterGLKN package.  

<h4> Load other dependencies and imports</h4>
The params csv was developed by GLKN staff manually matching parameter names between GLKN and METC datasets. The csv is posted on the GitHub repo. Note that the waterGLKN package already adds a column of parameter abbreviations following the same naming convention as the params.csv below.
```{r results = 'hide', warning = F, message = FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
params <- read.csv("https://raw.githubusercontent.com/KateMMiller/GLKN_MCES_analysis/refs/heads/main/data/GLKN_vs_METC_params_list_final.csv")
```

#### Compile Data
<h4> Download Data Package and import into R</h4>
Download the latest <a href="https://irma.nps.gov/DataStore/Reference/Profile/2309369"> GLKN Rivers Data Package</a>. The easiest way to do it is to download all as a zip. The file path below is where that zip is stored on Kate's machine and the name of the zip file. Then import the data package into R using the waterGLKN function `importData()`.
```{r results = 'hide'}
library(waterGLKN)
river_zip = "../data/GLKN_water/records-2309369.zip"
importData(type = 'zip', filepath = river_zip)
```


<h4> Filter Results.csv by Lake St. Croix sites and prepare data for binding with METC data. </h4>
```{r results = 'hide'}
# Site list
lksc <- c("SACN_STCR_20.0", "SACN_STCR_15.8", "SACN_STCR_2.0")
# pull in all results for Lk St. Croix sites
sacn <- getResults(park = "SACN", site = lksc, sample_type = "VS",
                   parameter = 'all',
                   months = 1:12,
                   sample_depth = 'all',
                   include_censored = T) |>
  select(Org_Code, Park_Code, Location_ID, Location_Name, sample_date, doy, year, month,
         depth_cat = Activity_Relative_Depth, depth = Activity_Depth, depth_unit = Activity_Depth_Unit,
         PARAMETER = Characteristic_Name, param_name, value, unit = Result_Unit)

sacn$param_name[sacn$param_name == "ChlA_ppb"] <- "ChlA_ugL"
sacn$unit[sacn$param_name == "ChlA_ppb"] <- "ug/l"

# convert depth in ft to m (they're actually all NULL, but in case other sites are in ft for later analysis)
sacn$depth[!is.na(sacn$depth) & sacn$depth_unit == "ft"] <- 
  sacn$depth[!is.na(sacn$depth) & sacn$depth_unit == "ft"] * 0.3048
sacn$depth_unit[sacn$depth_unit == "ft"] <- "m"
```

<h4> Prepare METC data for binding with GLKN data</h4>
Download all data from 2006 and later from the METC's <a href="https://eims.metc.state.mn.us/AdvancedSearch">Environmental Information Management Systems (EIMS)</a> web server for all monitoring locations within Lake St. Croix. The data for this analysis were downloaded on 3/18/2025.
```{r results = 'hide'}
# metc data from webserver
metc <- read.csv("./data/local/2025-03-18_1359_56_MCES_EIMS_data.csv")

# name sites based on Rick's stream distance method
metc1 <- metc |> 
  mutate(Location_ID = case_when(grepl("SC0003", STATION_ID) ~ as.character("METC_STCR_0.1"),
                                 grepl("SC0233", STATION_ID) ~ as.character("METC_STCR_23.6"),
                                 grepl("SC0234", STATION_ID) ~ as.character("METC_STCR_23.4"),
                                 grepl("82000100-08", STATION_ID) ~ as.character("METC_STCR_22.5"),
                                 grepl("82000100-06", STATION_ID) ~ as.character("METC_STCR_11.3"),
                                 grepl("82000100-03", STATION_ID) ~ as.character("METC_STCR_16.6"),
                                 grepl("82000100-05", STATION_ID) ~ as.character("METC_STCR_12.4"),
                                 grepl("82000100-04", STATION_ID) ~ as.character("METC_STCR_15.3"),
                                 grepl("82000100-01", STATION_ID) ~ as.character("METC_STCR_22.3"))) |>
  filter(!is.na(Location_ID)) # UM8128 is the only station that doesn't get matched with Rick's new LocIDs

metc1$Org_Code <- "METC"
metc1$Park_Code <- "METC"
metc1$sample_date <- format(as.Date(metc1$START_DATE_TIME, format = "%m/%d/%Y %H:%M"), format = "%Y-%m-%d")
metc1$year <- as.numeric(substr(metc1$sample_date, 1, 4))
metc1$month <- as.numeric(substr(metc1$sample_date, 6, 7))
metc1$doy <- as.numeric(format(as.Date(metc1$sample_date, format = "%Y-%m-%d"), "%j"))
metc1$depth_unit = "m"
metc1$depth_cat <- ifelse(metc1$SAMPLE_DEPTH_m <= 1, "surface", NA_character_)

metc2 <- metc1 |>
  mutate(value = ifelse(PARAMETER %in% c( "Chlorophyll-a, Pheo-Corrected",
                                           "Total Nitrate/Nitrite N, Unfiltered",
                                           "Total Phosphorus, Unfiltered"),
                                           RESULT/1000,
                                           RESULT)) |>
  select(Org_Code, Park_Code, Location_ID, Location_Name = NAME, sample_date, doy, year, month,
         depth_cat, depth = SAMPLE_DEPTH_m, depth_unit, PARAMETER, value, units = UNITS)

# Join METC data with param.csv for parameter abbreviations (param_name)
metc_join <- left_join(metc2, params, by = c("PARAMETER" = "Parameter", "units" = "Units")) |>
  filter(!is.na(New_Name)) |>
  select(Org_Code, Park_Code, Location_ID, Location_Name, sample_date, doy, year, month, depth_cat, depth,
         depth_unit, PARAMETER, param_name = New_Name, value, unit= units)

```

Keep only the parameters in common between GLKN and METC, then use row binding to combine the two datasets together.
```{r results = 'hide'}
# Determine parameters from METC that are on the params.csv and drop those missing.
metc_keep <- metc_join |> group_by(param_name) |> summarize(num_samps = sum(!is.na(value))) |> select(param_name) |> unique() |> c()

# SACN- only keep METC params
sacn2 <- sacn |> filter(param_name %in% metc_keep$param_name)
#table(sacn$param_name, sacn$Location_ID)

full_dat1 <- rbind(sacn2, metc_join) |> filter(year > 2006 & year < 2025) # GLKN sites only have data from 2007 - 2024
```

Compile USGS discharge data
```{r cache = T}
dischg <- renameNWISColumns(readNWISdv(siteNumbers = gages, parameterCd = "00060"))
gages <- c("05341550", "05344490")
dischg$Location_ID[dischg$site_no == gages[1]] <- "USGS_STCR_23.5"
dischg$Location_ID[dischg$site_no == gages[2]] <- "USGS_STCR_0.2"
dischg$month <- as.numeric(format(dischg$Date, "%m"))

dis_wide <- dischg |> select(-site_no) |>
  filter(month %in% 4:11) |> # filter only GLKN-sampled months
  pivot_wider(names_from = Location_ID, values_from = c(Flow, Flow_cd)) 

dis_wide_overlap <- dis_wide |> filter(!is.na(Flow_USGS_STCR_0.2) & !is.na(Flow_USGS_STCR_23.5))

dischg2 <- dischg |> filter(Date > as.Date("2011-09-09", format = "%Y-%m-%d"))

dp <- 
ggplot(dischg2, aes(x = Date, y = Flow, group = Location_ID, color = Location_ID)) + 
  geom_line() + theme_WQ() + labs(color = NULL) +
  scale_color_brewer(palette = "Set1")
```

Plot of discharge for overlapping sample periods of the stream gages.
```{r echo = F}
dp
```


Check on flow rating. Most are A, a few P (provisional). The 'e' refers to estimated. 
```{r}
table(dischg$Location_ID, dischg$Flow_cd)
```

Correlation in discharge between the two sites
```{r}
round(cor(dis_wide_overlap[,c("Flow_USGS_STCR_23.5", "Flow_USGS_STCR_0.2")]), 2)[1,2] # 0.96
```

```{r}
mod <- lm(Flow_USGS_STCR_0.2 ~ Flow_USGS_STCR_23.5, data = dis_wide_overlap)
summary(mod) # Slope is 0.96 Rsq 0.92. They're quite close. 
```


### Sampling Intensity {.tabset}
#### Code
```{r}
full_dat <- full_dat1 |> filter(!Location_ID %in% "METC_STCR_23.4") # 23.4 has a very narrow period of record. Dropping

full_dat$site_abbr <- factor(gsub("_STCR", "", full_dat$Location_ID),
                             levels = c("METC_23.6", #"METC_23.4", 
                                        "METC_22.5", "METC_22.3",
                                        "SACN_20.0", "METC_16.6", "SACN_15.8", "METC_15.3",
                                        "METC_12.4", "METC_11.3", "SACN_2.0", "METC_0.1"))

full_dat$site_order <- factor(full_dat$Location_ID, 
                              levels = c("METC_STCR_23.6", #"METC_STCR_23.4", 
                                         "METC_STCR_22.5", "METC_STCR_22.3",
                                         "SACN_STCR_20.0", "METC_STCR_16.6", "SACN_STCR_15.8", "METC_STCR_15.3",
                                         "METC_STCR_12.4",  "METC_STCR_11.3", "SACN_STCR_2.0", "METC_STCR_0.1"))

params_site_year <- full_dat |> group_by(Site = site_abbr, Parameter = param_name, Year = year, Org_Code) |> 
  summarize(Num_Samps = sum(!is.na(value)), .groups = 'drop') |> 
  arrange(Site, Parameter, Year)

params_site_year_wide <- params_site_year |> #filter(Num_Samps > 0) |> 
  pivot_wider(names_from = Site, values_from = "Num_Samps") |> 
  arrange(Parameter, Year)

cols <- names(params_site_year_wide[,4:ncol(params_site_year_wide)])
params_site_year_wide[,cols][params_site_year_wide[,cols] == 0] <- NA_real_

# sampling matrix 
psy_tab <- kable(params_site_year_wide, format = 'html', align = 'c', 
  cap = "Sampling matrix by site for every parameter and year. Values are number of non-QAQC samples within a year. Site codes start with 'METC' for Metropolitan Councial sites, and 'SACN' for GLKN-monitored sites. Numbers indicate the stream miles.") |> 
  kable_styling(fixed_thead = T, bootstrap_options = c("condensed"), full_width = F) |> 
  column_spec(1:ncol(params_site_year_wide), border_left = T, border_right = T) |> 
  collapse_rows(1, valign = 'top') 

params_site_year1 <- params_site_year |> mutate(num_samps_bin = case_when(between(Num_Samps, 1, 5) ~ 1,
                                                                          between(Num_Samps, 6, 10) ~ 2,
                                                                          between(Num_Samps, 11, 15) ~ 3,
                                                                          between(Num_Samps, 16, 20) ~ 4,
                                                                          Num_Samps > 20 ~ 5)) |> 
  filter(Num_Samps > 0)

# Create heat map of sampling intensity
psy_plot <- 
  ggplot(params_site_year1, aes(x = Site, y = Year)) +
    geom_tile(aes(fill = num_samps_bin), color = 'grey') + facet_wrap(~Parameter, ncol = 3) +
    scale_fill_distiller(palette = "Spectral", guide = "legend", name = "Num. Sample Bins", 
                         labels = c("Bin 1-5", "Bin 6-10", "Bin 11-15", "Bin 16-20", "Bin > 20")) +
    theme(axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0.5)) +
    waterGLKN::theme_WQ() +
    labs(x = NULL) +
    scale_y_continuous(breaks = c(2006, 2010, 2014, 2018, 2022))

params_site_year_month <- full_dat |> group_by(Site = site_abbr, param_name, year, month) |> 
  summarize(num_samps = sum(!is.na(value)), .groups = 'drop') |> filter(num_samps > 0)

# Plotting function to iterate through each parameter
param_heatmap <- function(dat = param_site_year_month, param = NA){
  p <-
    ggplot(dat, aes(x = Site, y = month)) +
    geom_tile(aes(fill = num_samps), color = 'grey') +
    facet_grid(rows = vars(year))+
    scale_fill_distiller(palette = "Spectral", guide = 'legend', 
                         name = "# samples") +
    theme(axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0.5)) +
    labs(x = NULL, y = NULL) +
    scale_y_continuous(breaks = seq(1, 12, 2), labels = c("Jan", "Mar", "May", "Jul", "Sep", "Nov"))

    return(p)
}

param_list <- sort(unique(full_dat$param_name))
```

#### Sampling Matrix

```{r echo = F}
psy_tab
```

#### Sampling Heat Maps {.tabset}
##### All Params
Main takeaways from sampling intensity: 
<ul>
<li>METC_STCR_23.6 and METC_STCR_0.1 collect the most data, and at a greater frequency within years than GLKN sites.</li>
<li>METC_STCR_22.5, METC_STCR_22.3, METC_STCR_16.6, METC_STCR_15.3, METC_STCR_12.4, METC_STCR_11.3 primarily only have water temperature, Secchi depth, and ChlA associated with them.</li>

<li>Parameters and sites to model for redundancy analyses </li>
  <ul>
  <li><b>ChlA_ugL</b>: Good overlap among all sites and years. Analyze for all sites. </li>
  <li><b>Cl_mgL</b>: Analyze for METC_23.6 and METC_0.1 (~continuous record); periodic samples in GLKN sites. </li>
  <li><b>DO_mgL</b>: Analyze for METC_23.6 and METC_0.1 (~continuous record); good coverage in GLKN sites. </li>
  <li><b>NO2+NO3_ugL</b>: Analyze for METC_23.6 and METC_0.1 starting in 2018.</li>
  <li><b>P_ugL</b>: Analyze for METC_23.6 and METC_0.1 (~continuous record); periodic samples in GLKN sites .</li>
  <li><b>pH</b>: Analyze for METC_23.6 and METC_0.1 (~continuous record); good coverage in GLKN sites. </li>
  <li><b>Secchi_m</b>: Good overlap among all sites and years. Analyze for all sites. </li>
  <li><b>SO4_mgL</b>: Analyze for METC_23.6 and METC_0.1 (biweekly until 2019); periodic samples in GLKN sites. no new records since 2016.</li>
  <li><b>SpecCond_uScm</b>: Analyze for METC_23.6 and METC_0.1 (~continuous record); good coverage in GLKN sites. </li>
  <li><b>TempWater_C</b>:  Good overlap among all METC sites and years. Analyze for all sites. SACN_15.8 is the only GLKN site with data past 2010.</li>
  <li><b>TSS_mgL</b>: Analyze for METC_23.6 and METC_0.1 (~continuous record); periodic samples in GLKN sites.</li>
  </ul>
  
<li>Parameters that may be included after first cut: </li>
<ul>
  <li><b>Alkalinity_mgL</b>: METC started collecting in METC_23.6 and METC_0.1 in 2017, but GLKN has record back to 2007. </li>
  <li><b>DOC_mgL</b>: METC started collecting in METC_23.6 and METC_0.1 in 2016, but GLKN has record back to 2007.  </li>

</ul>
  
<li>Parameters dropped from redundancy analysis with notes: </li>
  <ul>
  <li><b>Ca_mgL</b>: No new samples since 2020 in METC.</li>
  <li><b>DOsat_pct</b>: Not sampled by METC. Will use DO_mgL. </li>
  <li><b>K_mgL</b>: No new samples since 2020 in METC.</li>
  <li><b>Mg_mgL</b>: No new samples since 2020 in METC.</li>
  <li><b>Na_mgL</b>: No new samples since 2020 in METC.</li>
  <li><b>NH4_ugL</b>: No new samples since 2014 in METC.</li>
  <li><b>Si_mgL</b>: No new samples since 2021 in METC. </li>
  <li><b>Transp_cm</b>: No new samples since 2016in METC. </li>
  </ul>
</ul>

```{r echo = F, out.width = "100%", fig.height = 10, fig.cap="Heatmap of sampling intensity by site, parameter and year, such that blue bins were sampled 1-5 times within a given year and site, red bins more than 20 samples within a given year, etc. Sites or ordered by stream mile. Sites with METC are monitored by the MetCouncil. Sites with SACN are monitored by GLKN."}
psy_plot
```


```{r sym_heatmap_chunk, warning = F, message = F, eval = FALSE, echo = F}
p <- param_heatmap(dat = df, param = prm)
print(p)
```

```{r results = 'asis', fig.height = 10, echo = F}
for(i in seq_along(param_list)){
  prm <- param_list[[i]]
  df <- params_site_year_month |> filter(param_name %in% prm)
  cat("##### ", prm, "\n\n")
  cat(paste0("Heat map of number of samples collected in each year and month by site for <b>", prm, "</b>."))
  <<sym_heatmap_chunk>>
  cat("\n\n")
  cat("\n\n")
}

```


#### Final Params by Site Matrix
Creating data frame of site and parameter matrix for easier iteration later
```{r}
all_sites <- sort(unique(full_dat$site_order))
metc2_sacn <- c("METC_STCR_23.6", "SACN_STCR_20.0", "SACN_STCR_15.8", "SACN_STCR_2.0", "METC_STCR_0.1")

alk <- data.frame(Location_ID = metc2_sacn, param_name = "Alkalinity_mgL")
chla <- data.frame(Location_ID = all_sites, param_name = "ChlA_ugL")
cl <- data.frame(Location_ID = metc2_sacn, param_name = "Cl_mgL")
doc <- data.frame(Location_ID = metc2_sacn, param_name = "DOC_mgL")
do <- data.frame(Location_ID = metc2_sacn, param_name = "DO_mgL")
nox <- data.frame(Location_ID = metc2_sacn, param_name = "NO2+NO3_ugL")
p <- data.frame(Location_ID = metc2_sacn, param_name = "P_ugL")
ph <- data.frame(Location_ID = metc2_sacn, param_name = "pH")
sec <- data.frame(Location_ID = all_sites, param_name = "Secchi_m")
so4 <- data.frame(Location_ID = metc2_sacn, param_name = "SO4_mgL")
sc <- data.frame(Location_ID = metc2_sacn, param_name = "SpecCond_uScm")
tmp <- data.frame(Location_ID = all_sites, param_name = "TempWater_C")
tss <- data.frame(Location_ID = metc2_sacn, param_name = "TSS_mgL")

param_site_mat <- rbind(alk, chla, cl, doc, do, nox, p, ph, sec, so4, sc, tmp, tss)
head(param_site_mat)

```


```{r eval = F, echo = F, include = F}
write.csv(full_dat, "./data/local/GLKN_METC_combined_data.csv", row.names = F)
```

### Analysis
